A load balancing scheme for massively multiplayer online games

### 2009-04-29 trunk/textos/dissertation/MTAP_LaTeX/pub/tex/latex/svjour3/global/extremebalancing.tex

\begin{abstract}
MMOGs, or massively multiplayer online games, are applications which require much network bandwidth to function properly. In a distributed MMOG server architecture, with heterogeneous resources, the server nodes may become easily overloaded by the high demand from the players for state updates. Much work has been done in order to distribute the load on the server nodes, but this load is usually defined as the number of players on each server, what is not an ideal measure. Also, the heterogeneity of the system is frequently overlooked. In this work, we propose a balancing scheme which has two main goals: allocate load on the servers proportionally to the each one's power and reduce as much as possible the overhead from the distribution, considering the load as the occupied bandwidth of each server. It is divided in three phases: local selection of servers, balancing and refinement. Four algorithms were proposed, from which \ggp\ is the best for overhead reduction and \ggpf\ is the most suited for reducing player migrations between servers. We also make a review of related works and some comparisons were made, where our approach performed better.

@@

Ahmed's algorithm, in turn, presented the second highest average overhead. The most probable reason for this is the choice of the least loaded server to receive a microcell being transferred from an overloaded server. Though this is an obvious choice in terms of load balance, it does not consider that the chosen server may have no connection to that microcell, creating a fragmented region and, thus, increasing the overhead on the system.

@@

	\textbf{Carlos Eduardo Benevides Bezerra} is a full-time Ph.D. student at UFRGS (Universidade Federal do Rio Grande do Sul). He obtained his M.Sc. from the same university in 2009 and his B.Sc. degree from UFBA (Universidade Federal da Bahia) in 2007.
%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:cebb}       % Give a unique label
\end{figure}

@@

  \textbf{Cláudio Fernando Resin Geyer} is a full-time Professor at UFRGS.
%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:cebb}       % Give a unique label
\end{figure}

>>>>

\begin{abstract}
In a distributed MMOG massively multiplayer online game) server architecture, the server nodes may become easily overloaded by the high demand from the players for state updates. Many works propose algorithms to distribute 
%51
the load on the server nodes, but this load is usually defined as the number of players on each server, what is not an ideal measure. Also, the possible heterogeneity of the system is frequently overlooked. We propose a balancing scheme with two main goals: allocate load on server nodes proportionally to the each one's power and 
%111
reduce as much as possible the inter-server communication overhead, considering the load as the occupied bandwidth of each server. It is divided in three phases: local selection of servers, balancing and refinement. Four algorithms were proposed, from which \ggp\ is the best for overhead reduction and \ggpf\ is the most suited for reducing player migrations between servers. We also make a review of related works and some comparisons were made, where our approach performed better.

@@

Ahmed's algorithm, in turn, presented the second highest average overhead. The most probable reason for this is the choice of the least loaded server to receive a microcell being transferred from an overloaded server. Though this is an obvious choice in terms of load balance, it does not consider that the least loaded server may have no microcell adjacent to the microcell being transferred, creating a fragmented region and, thus, increasing the overhead on the system.

@@

	\textbf{Carlos Eduardo Benevides Bezerra} is a full-time Ph.D. student at UFRGS (Universidade Federal do Rio Grande do Sul). He obtained his M.Sc. from the same university in 2009 and his B.Sc. degree from UFBA (Universidade Federal da Bahia) in 2007. His research interests are massively multiplayer online games, interest management algorithms, parallel and distributed algorithms, peer-to-peer networks and computational geometry.
%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:cebb}       % Give a unique label
\end{figure}

@@

  \textbf{Cláudio Fernando Resin Geyer} is an associate professor at the Informatics Institute of the Federal University of Rio Grande do Sul. His research interests include massively multiplayer games, grid computing and ubiquitous computing. He received his Ph.D. in informatics from Joseph Fourier University. He is a member of ACM and of the Brazilian Computer Society.

%% figure caption is below the figure
%\caption{Please write your figure caption here}
\label{fig:cebb}       % Give a unique label
\end{figure}
